### 2022-01-20 manuscript.rmd
Make room for the WJS example

Communication research is often comparative, journalism studies are no exception. For example, comparative approach is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI;@grasland:2019:I], among others. A typical comparative study in journalism research, otherwise known as comparative content analysis, includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation), namely, the article-level.

@@

In our paper we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies. While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p. 121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Using the openly available *useNews* data and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis.

@@

Comparative research in journalism studies, unlike randomized surveys or randomized media experiments, usually collects all available data. In contrast to sampling, these studies are actually doing census of all data and there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p. 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.

@@

@@

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method [e.g. @kovic:2017:B;@chan2020high] these studies are not comparative. As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT. We believe comparative communication research fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to practically implement one using the R package *brms* [@burkner2017advanced]. As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.

# Methods

We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a typical Bayesian multilevel regression analysis. The analysis was guided by a classic question in news value research: Does the distance between China and the host country of a media outlet increase the frequency of China coverage? In other words, we studied the ecological effect of the distance from China on the frequency of China coverage. Several distance measures were used to formulate our pre-registered hypotheses: physical distance between two capitals, trade volume between two countries, and cultural distance between two societies.

@@

### Priors

@@

# Regression results

@@

## Diagnosis of convergence

@@

## Further diagnostics

@@

# Discussion

Instead of arguing the advantages of Bayesian multilevel regression analysis once again like we did in the introduction, we propose several extensions to the above barebone analysis. The analyses in these extensions are not preregistered.

## Extension #1: Hypothesis testing

@@

## Extension #2: Cross-level interaction

@@

## Extension #3: Current study as the informative prior for the next study

@@

@@

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research. We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Researchers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Model B1). Still, eventually it worked and typical studies in comparative journalism research [e.g. 6,525 articles in @esser:2013:C] can be estimated within a reasonable time frame [^TIME].

>>>>

Communication research is often comparative, journalism studies are no exception. For example, comparative approach is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI;@grasland:2019:I], among others. A typical comparative study in journalism research, otherwise known as comparative content analysis, includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Surveys in journalism research are often comparative, e.g. the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC].

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles or behaviours of journalists. For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation), namely, the article-level or journalist-level.

@@

In our paper we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies. While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p. 121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Using the openly available *useNews* and WJS datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.

@@

Comparative content analytic studies in journalism studies, unlike randomized surveys or randomized media experiments, often collect all available data. In contrast to sampling, these studies are actually doing census of all data. There is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p. 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.

@@

Before we move on to the next section, it is important to point that **non-stochastic data is not an essential condition for applying the Bayiesan approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets. Therefore, one can analyse both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.

@@

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method [e.g. @kovic:2017:B;@chan2020high] these studies are not comparative. As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT. We believe comparative communication research fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced]. As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.

The two examples below show how the Bayesian multilevel regression analysis can be deployed to the common archtypes of comparative journalism studies. The first example is an analysis of a comparative, non-stochastic content analytic dataset. The second example is an analysis of a comparative, stochastic survey dataset.

# Example 1: useNews

We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a typical Bayesian multilevel regression analysis on a nonstochastic comparative dataset. The analysis was guided by a classic question in news value research: Does the distance between China and the host country of a media outlet increase the frequency of China coverage? In other words, we studied the ecological effect of the distance from China on the frequency of China coverage. Several distance measures were used to formulate our pre-registered hypotheses: physical distance between two capitals, trade volume between two countries, and cultural distance between two societies.

@@

## Priors

@@

## Regression results

@@

### Diagnosis of convergence

@@

### Further diagnostics

@@

## Extentions

We propose several extensions to the above barebone analysis. The analyses in these extensions are not preregistered.

### Extension #1: Hypothesis testing

@@

### Extension #2: Cross-level interaction

@@

### Extension #3: Current study as the informative prior for the next study

@@

# Example 2: The Worlds of Journalism study

Example 1 above demonstrated how to conduct a Bayesian multilevel regression analysis. In this example, the same approach is applied to a stochastic dataset from a randomize survey.

@@

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research. We demonstrate using the openly available useNews and WJS datasets that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Researchers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Example 1, Model B1). Still, eventually it worked and typical studies in comparative journalism research [e.g. 6,525 articles in @esser:2013:C] can be estimated within a reasonable time frame [^TIME].
